What can GitHub and Googlecode Issues tell us about Exceptions in Android and Java?

### 2014-09-01 android-stacks.tex
including more data from manual inspections of CG collected by Lucas

\subsection{Manual Inspections}
This study was also based in a set of manual inspection tasks. Besides the 
 identification of Android projects details previously. 
Manual inspections were used discover the type of exceptions thrown by 
the applications and libraries we manually inspect the sourcecode or javadoc
 documentation of each of them. When the exception was removed from the 
last app version, the previous versions were analyzed. When the exception was
 not found on the previous versions, the exception was discarded.  Only 3 exceptions 
remained undefined and were removed from this study.

@@

\begin{table*}
  \centering
  \begin{tabular}{rcccccccc}
    \hline
    \bfseries{Root Exception} &  \multicolumn{2}{c}{\bfseries{Projects (GH/CG)}} &  \multicolumn{2}{c}{\bfseries{Occurrences (GH/CG)}} & \textsf{Android} & \textsf{Libcore} & \textsf{App} & \textsf{Lib} \\
    & \bfseries{\#} &  \bfseries{\%} & \bfseries{\# } & \bfseries{\% } &&&&\\
    \hline
java.lang.NullPointerException            & 254 /  78  & 52,70\%  & 1225 / 439  & 30,08\% & 473 /  26  & 18 & 595 & 137 \\  %LIBORAPP=408
java.lang.IllegalStateException          & 99 / 21  & 20,54\%  & 234 / 44  & 5,75\%  & 165 & 12 & 36  & 20  \\
java.lang.IllegalArgumentException          & 94 / 48  & 19,50\% & 255 / 98  & 6,26\% & 146 & 6  & 64  & 39   \\
java.lang.RuntimeException                & 91 / 31 & 18,88\% & 232 / 87  & 5,70\%  & 167 & 1  & 47  & 17   \\
java.lang.OutOfMemoryError                 & 56  / 22  & 11,62\% & 180 / 57 & 4,42\% & 121 & 15 & 17  & 23   \\
java.lang.NoClassDefFoundError           & 52  / 15 & 10,79\%  & 73 / 21   & 1,79\%  & 9   & 0  & 37  & 26   \\
java.lang.ClassCastException             & 49  / 15 & 10,17\%  & 94 / 36   & 2,31\%  & 43  & 0  & 40  & 11   \\
java.lang.IndexOutOfBoundsException       & 47  / 15 & 9,75\%   & 127 / 39  & 3,12\% & 47  & 0  & 71  & 8    \\
java.lang.NoSuchMethodError               & 40 / 14  & 8,30\%  & 57 / 23  & 1,40\%  & 9   & 0  & 39  & 9   \\
java.util.ConcurrentModificationException & 38 / 5 & 7,88\% & 54 / 11  & 1,33\%   & 5   & 0  & 43  & 6   \\

@@

@@

Runtime	&	1075	&	56	&	1446	&	374	&	2951\\
Error	&	144	&	34	&	168	&	105	&		451	\\
Checked	&	110	&	230	&	139	&	145	&	624	\\
Throwable	&	0	&	0	&	1	&	0	&	1	\\
Undefined	&	1	&	0	&	6	&	8	&	15	\\
    \hline
All		& 1330	&	320	&	1760	&	632	&	4042	\\
    \hline
  \end{tabular}
\caption{Types of root exceptions.}
  \label{tab:typeroottab}
\end{table}

>>>>

\subsection{Manual Inspections}
This study was also based in a set of manual inspection tasks. Besides the 
 identification of Android projects details previously. 
Manual inspections were used discover the type of exceptions thrown by 
the applications and libraries we manually inspect the sourcecode or javadoc
 documentation of each of them. When the exception was removed from the 
last app version, the previous versions were analyzed. When the exception was
 not found on the previous versions, the exception was discarded.  Only 31 exceptions 
remained undefined which were reported on 61 exception stack traces (as presented in Table ~\ref{tab:typeroottab}).

@@

%SELECTS:
%SELECT COUNT(distinct(repo)) FROM STACKTRACESUMMARY WHERE MAIN_CAUSE LIKE '%java.lang.NullPointerException%'
%and repo !='android';

%SELECT COUNT(*) FROM STACKTRACESUMMARY WHERE MAIN_CAUSE LIKE '%java.lang.IllegalStateException%'
%and repo !='android' AND MAINSIGNALER_FROM LIKE '%ANDROID%';

\begin{table*}
  \centering
  \begin{tabular}{rcccccccc}
    \hline
    \bfseries{Root Exception} &  \multicolumn{2}{c}{\bfseries{Projects (GH/CG)}} &  \multicolumn{2}{c}{\bfseries{Occurrences (GH/CG)}} & \textsf{Android} & \textsf{Libcore} & \textsf{App} & \textsf{Lib} \\
    & \bfseries{\#} &  \bfseries{\%} & \bfseries{\# } & \bfseries{\% } &&&&\\
    \hline
java.lang.NullPointerException            & 254 /  78  & 52,70\%  & 1225 / 439  & 30,08\% & 473 /  26  & 18 /  & 595 / 241 & 137 / 169 \\  %LIBORAPP=408
java.lang.IllegalStateException          & 99 / 21  & 20,54\%  & 234 / 44  & 5,75\%  & 165 / 15 & 12  / 0 & 36  / 5 & 20 / 24  \\
java.lang.IllegalArgumentException          & 94 / 48  & 19,50\% & 255 / 98  & 6,26\% & 146 / 41 & 6 / 0 & 64 / 31  & 39  / 26  \\
java.lang.RuntimeException                & 91 / 31 & 18,88\% & 232 / 87  & 5,70\%  & 167 / 33 & 1 / 0 & 47 / 17 & 17 / 37   \\
java.lang.OutOfMemoryError                 & 56  / 22  & 11,62\% & 180 / 57 & 4,42\% & 121 / 18 & 15 / 0 & 17 / 18  & 23 / 13  \\
java.lang.NoClassDefFoundError           & 52  / 15 & 10,79\%  & 73 / 21   & 1,79\%  & 9 / 1   & 0 / 0  & 37 / 9  & 26 / 11   \\
java.lang.ClassCastException             & 49  / 15 & 10,17\%  & 94 / 36   & 2,31\%  & 43 / 3  & 0  / 0 & 40 / 15  & 11 / 18  \\
java.lang.IndexOutOfBoundsException       & 47  / 15 & 9,75\%   & 127 / 39  & 3,12\% & 47 / 2  & 0/0  & 71/22  & 8 / 14    \\
java.lang.NoSuchMethodError               & 40 / 14  & 8,30\%  & 57 / 23  & 1,40\%  & 9  /  0  & 0  / 0 & 39 /  17    & 9 / 6  \\
java.util.ConcurrentModificationException & 38 / 5 & 7,88\% & 54 / 11  & 1,33\%   & 5  / 0  & 0  / 0 & 43 / 3 & 6 / 7  \\

@@

%SELECT COUNT(*) FROM STACKTRACESUMMARY WHERE
% repo !='android'  AND MAIN_EXTENDS LIKE 'RUNTIME%'

@@

Runtime	&	1075 	&	56	&	1446	&	374	&	2951 / 956\\
Error	&	144	&	34	&	168	&	105	&		451 /  250	\\
Checked	&	110	&	230	&	139	&	145	&	624  /  734	\\
Throwable	&	0	&	0	&	1	&	0	&	1 / 1	\\
Undefined	&	1	&	0	&	6	&	8	&	15 / 46	\\ %22 DISTINCT EXCEPTIONS AND 9 IN GIT
    \hline
All		& 1330	&	320	&	1760	&	632	&	4042	\\
    \hline
  \end{tabular}
\caption{Types of root exceptions.}
  \label{tab:typeroottab}
\end{table}
